Argennon: A Scalable Smart Contract Platform

### 2021-07-20 tex/sections/elements.tex
Fix some readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

For example \texttt{21.255.37}, \texttt{0} and \texttt{1.0.0.0.0}, are valid application addresses.

@@

\begin{itemize}
    \item Installation of AVM smart contracts and determining the update policy of a smart
    contract: if the contract is updatable or not, which accounts can update or uninstall the contract, and so
    on.
    \item Removing AVM smart contracts.
    \item Updating an AVM smart contract (if allowed).
\end{itemize}

@@

As a result, every Argennon transaction contains two HTTP requests. Besides these HTTP requests, the
transaction is required to contain a resource declaration object, specifying the maximum amount of resources
it needs for execution.

@@

Every Argennon transaction is required to specify a cap for all the resources it needs. This
includes memory, network and processor related resources. When a transaction reaches one of its
pre-declared resource caps, executing any AVM instruction which uses that resource, will result in an AVM exception.

As we know, every Argennon transaction consists of two \texttt{i\_invoke\_dipatcher} instructions. The first
instruction is always considered as a \emph{free} instruction and resources spent during its execution
session will not be counted. Thus, only the second instruction could fail due to exceeding resource limits.

The Argennon protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.}. The remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum costs, executing any instruction which has
that type of cost, will throw an AVM exception.

\note{When a transaction reaches its \texttt{maxExternalCost}, it can still keep executing
its own code, while it can not call other smart contracts.
This way the execution cost of a smart contract is completely decoupled from the
smart contract it calls, and a malicious contract can not make its invoker fail
by using infinite loops.}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://app.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 77

>>>>

For example \texttt{21.255.37}, \texttt{0}, \texttt{11.6} and \texttt{2.0.0.0.0}, are valid application addresses.

@@

\begin{itemize}
    \item Installation of AVM smart contracts and determining the update policy of a smart
    contract: if the contract is updatable or not, which accounts or smart contracts can update or uninstall
    the contract, and so on.
    \item Removing an AVM smart contract (if allowed).
    \item Updating an AVM smart contract (if allowed).
\end{itemize}

@@

As a result, every Argennon transaction contains two HTTP requests. Besides these HTTP requests, the
transaction is also required to contain a resource declaration object, specifying the maximum amount of resources
it needs for execution.

@@

Every Argennon transaction is required to specify a cap for all the resources it needs. This
includes memory, network and processor related resources. If during emulation, a transaction reaches one of its
pre-declared resource caps, executing any AVM instruction which uses that resource, will result in an AVM exception.

As we know, every Argennon transaction consists of two \texttt{i\_invoke\_dipatcher} instructions. The first
instruction is always considered as a \emph{free} instruction and resources spent during its execution
session will not be counted. Therefore, only the second instruction could fail due to exceeding resource limits.

The Argennon protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.}. The remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum execution costs, executing any instruction
which has that type of cost, will throw an AVM exception.

\note{When a transaction reaches its \texttt{maxExternalCost}, it can still execute
its own code, while it can not call other smart contracts.
This way the execution cost of a smart contract is completely decoupled from the
smart contract it calls, and a malicious contract can not make its invoker certainly fail
by using infinite loops.}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://dapp.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 77
